---
title: "Female in Top Management"
subtitle: "-- from World Bank Data"
author: "Kejing Li"
institute: "UChicago"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      autoplay: 30000
      countdown: 30000
    
      
---
class: inverse, center, middle

# Introduction 

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE )
library(tidyverse)
```

---
class: center, middle

>“Gender inequality is not only a pressing moral and social issue, but also a critical economic >challenge.”     — McKinsey Global Institute

---
class: center, middle

This report intends to explore the female representation in top management. 

--

Four variables from the world bank database

- High-technology exports (% of manufactured exports)

--

- Firms with female top manager (% of firms)

--

- Firms with female participation in ownership (% of firms)

--

- Start-up procedures to register a business 

???
Gender inequality is a commonplace talk of an old scholar. However, in recent years, the phenomenon is discussed under a new context - leadership in business. Incessant evidences suggest that the gender diversity contributes to the bussiness operation. To better understand the current development, this report analyzes four variables from the world bank database

```{r, include = FALSE}
read_and_tidy <- function(file) {
  read_csv(file, skip = 4) %>%
 #select & filter data needed for analysis
  select(-c("Country Code", "Indicator Name","X64"))%>%
  rename(country = "Country Name",
      indicator_code = "Indicator Code") %>%
  filter(indicator_code %in% c("IC.FRM.FEMO.ZS",
                               "IC.FRM.FEMM.ZS",
                               "IC.REG.PROC.FE",
                               "TX.VAL.TECH.MF.ZS")) %>%
  #put each observations in row, each variables in its columns
    pivot_longer(-c(country,indicator_code),
                 names_to = "year",
                 values_to = "Value",
                 names_ptypes = list(year = double())) %>%
    pivot_wider(names_from = indicator_code,
                values_from = "Value") %>%
  #remane the code in to infomative names
    rename(hitech_export = "TX.VAL.TECH.MF.ZS",
           female_register_procedure = "IC.REG.PROC.FE",
           female_ownership_participation = "IC.FRM.FEMO.ZS",
           female_top_management = "IC.FRM.FEMM.ZS")
}
```

```{r, include = FALSE, cache = TRUE}
# silent the warning message
economies <- dir(path = "data_world_bank", full.names = TRUE)

# run on all economies using a map function
data <- map_df(economies, read_and_tidy)

```

---
class: inverse, center, middle

# Explore the data

---
# Firms with female participation in ownership by year

```{r ownership}
data %>%
  drop_na(female_ownership_participation)%>%
  group_by(year) %>%
  summarize(female_ownership_participation = mean(female_ownership_participation)) %>%
  ggplot()+
  geom_col(aes(year,female_ownership_participation/100))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  scale_x_continuous(breaks = 2004:2018)+
  labs(title = "Firms with female participation in ownership",
        x = "year",
        y = "% of firms")
```

???
As shown below, the data start merely from the 21 century when the phenomenon came into the public attention. But the overall trend doesn't appear any upward nor downward trend over the period. Whatever the variation, less than half of the firms have female participated in the ownership.

---

# Firms with female top manager by year

```{r top manager}
data %>%
  drop_na(female_top_management)%>%
  group_by(year) %>%
  summarize(female_top_management = mean(female_top_management)) %>%
  ggplot()+
  geom_col(aes(year, female_top_management/100))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  scale_x_continuous(breaks = 2007:2018)
  labs(title = "Firms with female top manager",
        x = "year",
        y = "% of firms")
```

???
As like the female participation in ownership data, percentage of firms with female manager don't have apparent trend over the years concerned, but with a even lower average, fluctuating between 10% to 20%. Females are largely underrepresented in the top management.

---

# Relationship between female participation in ownership and female top manager

```{r}
data%>%
  drop_na(female_ownership_participation, female_top_management) %>%
  group_by(country)%>%
  ggplot()+
  geom_smooth(aes(female_top_management/100,female_ownership_participation/100))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))+
  labs(title = "Relationship between female participation in ownership and female top manager",
        x = "Female top manager",
        y = "Female participation in ownership")

```

???
Since neither the percentage of female in top mangement nor female participation in ownership alone indicate any trend along the years. Doubts arise whether these two variables are telling the same story. Covariance analysis is hereby given that demonstrates these two variables are positively related to each other. Where females appear more often as top managers, female participation in ownership is correspondingly higher. This result suggests the position of female in leadership is consistent across different measurements.

---

class: center, middle

# Thanks!

Slides created via the R package
[**xaringan**](https://github.com/yihui/xaringan).


